\documentclass{wst}
\title{By-Laws to the Articles of Incorporation Of The Wildwood Summer Theatre}

\begin{document}
\maketitle

\section{Definition of Season and Year}
\begin{outline}[enumerate]
\1 The theatre season shall begin with the call-to-order of the official Critique meeting of the Board of Directors and shall end with the call-to-order of the following Critique Meeting of the Board of Directors (as specified in By-Law II.A.).
\1 The theatre year shall be defined as June 1 of any given year through May 31 of the following year.
\1 Instances where these terms are important are specified in an addendum to these Articles entitled ''Wildwood Summer Theatre Season and Year''.

\section{Operation of the Board of Directors: Meeting Times}
\1 The Board of Directors shall conduct official meetings of the Board of Directors at the following times.  Agendas for these official meetings may be found in an addendum to these By-Laws entitled "Wildwood Summer Theatre Official Board Meeting Agendas".
\2 Critique Meeting: no less than 7 days and no more than 21 days after the close of the previous season's production.
\2 Fall Meeting: on the Friday, Saturday, or Sunday following Thanksgiving Day.
\2 Winter Meeting: between December 27 and January 5.
\2 Spring Meeting: between March 1 and April 15, to be set definitely by the Chairman when the greatest number of Board members will be able to attend.
\2 Summer Meeting: within 12 days prior to the close of the season's production.
\1 The Board of Directors shall conduct an official meeting of the current membership of the Association prior to the Critiqueofficial meeting of the Board of Directors.  The agenda for this official meeting may be found in an addendum to these By-Laws entitled "Wildwood Summer Theatre Association Critique Meeting Agenda.
\1 Notification of official meetings of the Board of Directors and official meetings of the Association shall be made at least 2 weeks prior to the scheduled date of the meeting.
\1 The Board of Directors may also conduct provisional meetings at any times it deems necessary, provided every member of the Board is given at least 24 hours notice as to the date, time, and location of the meeting by the Chairman, Parliamentarian, or Secretary of the Board.
\1 Official Board business, especially voting on issues, may be conducted only in an actual meeting.  Electronic communication is permissible for discussion.
\2 Should a Board member’s  schedule prohibit physical attendance at a board meeting, videoconferencing shall be an acceptable alternative to physical attendance provided said Board member devotes their full attention to the meeting. A Board member may use this method of attendance once in a 12-month period without penalty as per Article V, Section B, Paragraph
\3 Video conferencing Board members may vote only if there is quorum at the actual location of the board meeting .  
\end{outline}

\section{Operation of the Board of Directors: Structure}
A.	The Board of Directors shall elect a Chairman from its tenured members whose term of office shall be one year. The Chairman shall be at least 18 years of age and have been a member of the Board for at least 12 months.
B.	The Board of Directors shall elect a Parliamentarian from its tenured members whose term of office will be one year.  The Parliamentarian shall be at least 18 years of age and have been a member of the Board for at least 12 months.
C.	The Board of Directors shall elect a Treasurer from its tenured members whose term of office will be one year, effective immediately following the Summer Board Meeting.  The Treasurer shall be at least 18 years of age and have been a member of the Board for at least 12 months.
D.	The Board of Directors shall elect an Alumni Liaison from its tenured members whose term of office will be one year.
E.	The Board of Directors shall elect a Secretary from the Association whose term of office will be one year.
F.	The Board of Directors shall elect a Director of Development from its members whose term of office will be one year.
G.	Nominations shall be taken for tenured members of the Board at any official meeting when openings occur in its membership; although the Board may fill any openings at any time, it is not required to elect a new member at that time, provided that the requirements of Article V, Section A, Sub-section 1, Sub-sub-section (a) of the Articles of Incorporation are met.
H.	If an Annual Board Member must relinquish his/her position, that position shall remain vacant for the remainder of the theatre season.
I.	Should an emergency arise within the company that is immediate (immediate being defined as needing a resolution before the Board is able to convene and vote on the issue) the Board Chairman is given the authority to act on behalf of the Board of Directors.  Any decision that is made may be reviewed and overturned at the next available time by all present and voting members if deemed necessary.  Situtions and the extent of the emergency powers shall be defined by an addendum to these By-Laws entitled “Job description: The Board of Directors.”

\section{Operation of the Board of Directors: Rules of Order}
A.	The rules contained in Robert's Rules of Order shall govern the operation of the Board in all cases in which they are applicable, and in which they are not inconsistent with the Articles of Incorporation, By-Laws, or addenda to the Articles or By-Laws.
B.	The Board of Directors may choose to go into executive session, wherein only Board members and the Secretary may be present to hear debate.  The Board of Directors must go into executive session when electing new tenured board members, reviewing a Board membership, or interviewing and selecting staff.
C.	The Board of Directors does not accept proxy votes or absentee ballots.
D.	The purpose of the Board of Directors shall be defined by an addendum to these By-Laws entitled "Job Description: The Board of Directors.

\section{Selection of Staff}
A.	Board-selected Staff Positions
The Board of Directors shall appoint the following positions: Producer, Director, Production Manager, Production Stage Manager, Musical Director, Conductor, Choreographer, Technical Director, Scenic Designer, Lighting Designer, Sound Designer, Property Designer, Costume Designer, Make-Up/Hair Designer, Director of Public Relations, and Director of Fundraising.
B.	Other Staff Positions
1.	The Producer shall appoint, as deemed necessary, the following positions: Associate Producer(s) and Business Manager.
2.	The Director shall appoint, as deemed necessary, the Assistant Director(s) and/or Dramaturg.
3.	The Production Stage Manager shall appoint the Assistant Stage Manager(s) and Deck Manager(s).
4.	The Technical Director, in conjunction with the Designers, shall appoint, as deemed necessary, the following positions: Assistant Technical Director, Master Carpenter, Scenic Artist, Master Electrician, Audio Engineer, Costumer, Property Master, and Make-Up Crew Chief.
5.	The Director of Public Relations shall appoint, as deemed necessary, the following positions: Assistant Director of Public Relations, House Manager, Graphic Designer, Program Coordinator, Photographer, Director of Audience Development and Director of Recruitment.
6.	The Director of Fundraising shall appoint, as deemed necessary, the Assistant Director of Fundraising.
7. The Business Manager shall appoint, as deemed necessary, the Box Office Manager.
8. The Musical Director shall appoint, as deemed necessary, the Vocal Director.
C.	If, for any reason, the board decides to leave vacant any of the “Big Four” staff positions (Producer, Director, Director of Fundraising, Director of Public Relations), chosen at the Board Critique meeting, the board may elect to the position an interim replacement from the board of directors.  At the next board meeting this placement must then be confirmed, the title transferred to a new replacement, or their status as an interim continued.     
D.	If, for any reason, any Board-selected staff position remains or becomes vacant after the official Spring meeting of the Board of Directors, the Producer may fill the vacancy with the consent of the Board implied.
E.	Any staff member not specified in Section B may appoint an assistant if deemed necessary.

\section{Duties of the Producer}
The Producer shall:
A.	Hold authority and responsibility regarding the Production and the Association unless otherwise specified by the Articles of Incorporation or the By-Laws to the Articles of Incorporation.
B.     Be authorized to sign for the Association.
C.	Act as the Board of Directors' representative with respect to membership as set forth in Article X of the Articles of Association.
D.	With the advice and consent of the Board, determine the theatre location, performance dates, ticket prices, compensation for services rendered, and necessary capital investments.
E.	Conduct a final staff meeting after the opening of the show, but prior to its closing, the purpose and agenda of which is outlined in an addendum to these By-Laws, entitled, “Wildwood Summer Theatre Staff Critique Meeting.”

\section{Selection of Show(s)}
In any given year, the Board of Directors shall select its production(s) from a list of no fewer than five and no more than six theatrical works that will be provided to it by the Producer and the Director.  No such work shall be submitted by the staff, nor selected by the Board, that has been produced by the Theatre within the previous 12 years.

\section{Membership Dues}
Membership dues shall be paid by every member of the Association.  The Producer, in special cases, and at its discretion, may waive the payment of these dues with the consent of the Board.  Membership dues shall not exceed \$50 per person. The dues are not refundable after June 1st.

\section{Control of Funds}
\1 The Producer and Board Treasurer shall be the signatories to the Theatre's sole banking account.  The authorization of either of them shall be sufficient for the withdrawal of funds.
\1 At the official Spring meeting of the Board of Directors, the Producer shall submit his or her proposed budget for the present season.  The Board shall then discuss the proposed budget and determine a reasonable spending limit, with the understanding that the Producer is authorized to exceed that limit by 10\% should he deem it necessary.   While it is not the responsibility of the Board to approve individual lines of the budget, it is necessary to consider the entire document, so that a reasonable spending limit for the season can be agreed upon.

\section{Operation of the Staff}
The operation of the staff shall be guided by an addendum to these By-Laws entitled "Wildwood Summer Theatre Production Handbook".

\section{Notices}
Any notice required to be given pursuant to these By-Laws may be given by mail, private messenger, e-mail, facsimile, or in any other reasonable manner, in writing.

\end{document}
